Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-07-26 SupportingInformation.Rmd
adding pedagog figure

>>>>

```{r call_cop_pedag_fig,echo=F,results="hide",cache=T, cache.extra=list(seed,mtime("copula_pedag_fig.R"))}
set.seed(seed)
source("./copula_pedag_fig.R")

#cat(paste("start-time: ",Sys.time(),"\n"))
df<-cop_est_2par(fam=7,p1range = c(0.01:7),p2range = c(1:7),incr = 0.005)
saveRDS(df,"./Results/df_fam7_incr_0.005.RDS")
#cat(paste("stop-time: ",Sys.time(),"\n"))

df_fam7<-readRDS("./Results/df_fam7_incr_0.005.RDS")
#range(df_fam7$LTmUT)

pdf("copula_pedagog_fig_BB1_incr_0.005.pdf",height=8,width=20)
op<-par(mfrow=c(2,5),mar=c(3,3,3,3), mgp=c(1.5,0.5,0))

df_fam7_scr<-screening_df(df=df_fam7,ncut=5,Tau0=0.4,eps=1e-3,
                               LTmUT_vector_given = F,my_LTmUT_vector = NA)

df_fam7_screened<-df_fam7_scr$df_screened
df_fam7_LTmUT_vector<-df_fam7_scr$LTmUT_vector

for(i in 1:length(df_fam7_screened$LTmUT)){
  c<-BiCopSim(500,family=7,par=df_fam7_screened$par[i],par2=df_fam7_screened$par2[i])
  plot(c[,1],c[,2],col="red",xlab="u",ylab="v",cex.lab=2,cex.axis=1.5)
  mtext(paste0("tau = ",round(df_fam7_screened$Tau[i],4),
               ", LTmUT = ",round(df_fam7_screened$LTmUT[i],4),sep=""),side=3)
}

df_fam7_scr<-screening_df(df=df_fam7,ncut=5,Tau0=0.8,eps=1e-3,
                               LTmUT_vector_given = T,my_LTmUT_vector = df_fam7_LTmUT_vector)
df_fam7_screened<-df_fam7_scr$df_screened

for(i in 1:length(df_fam7_screened$LTmUT)){
  c<-BiCopSim(500,family=7,par=df_fam7_screened$par[i],par2=df_fam7_screened$par2[i])
  plot(c[,1],c[,2],col="red",xlab="u",ylab="v",cex.lab=2,cex.axis=1.5)
  mtext(paste0("tau = ",round(df_fam7_screened$Tau[i],4),
               ", LTmUT = ",round(df_fam7_screened$LTmUT[i],4),sep=""),side=3)
}
